A Multi-telescope Campaign on FRB 121102: Implications for the FRB Population

### 2017-07-18 referee_response.txt

General comments:

We thank the referee for a thoughtful review and suggestions for improvement.

@@

http://journals.aas.org/authors/aastex/aasguide60.html#celestial_objects

Please also use the full references for the items noted under the \software command, e.g.

emcee (Foreman-Mackey et al. 2013)

>>> Done. Thanks for the reminder.
>>> We accidentally left the latex shortcut for the source name ("\frb") in the title during submission. That has been changed to the full name, "FRB 121102".

@@

1. Throughout the text it is mentioned that this is the first simultaneous detection of an FRB pulse at multiple observatories, but I don't believe this is correct. The observations detailed in Marcote et al. 2017 include VLBI observations of individual pulses from FRB 121102 detected at different observatories. In that sense, this paper does not present the first simultaneous detection. Perhaps the authors mean first simultaneous detection at multiple radio frequencies, but if this is the case this statement should be revised throughout the manuscript.

>>> I do believe the VLA+AO burst is the first of its kind both as a multi-frequency and as a multi-telescope detection. The first VLA+Arecibo burst was detected on 17 September, while the bursts reported in Marcote et al were detected on 20 September. The publication date of the VLA+AO (discussed in Chatterjee et al 2017) and EVN bursts were simultaneous, so it is also not true that one was published first. I would prefer to keep the current wording.

2. While the simultaneous detection of an FRB pulse at multiple frequencies is indeed quite interesting I would argue that the _non-detections_ while observing with the VLA and other telescopes is also extremely important and stick out to me as a key result of this paper. This isn't well highlighted in the abstract or the text of the paper and throughout the manuscript these non-detections are not presented in a straightforward way. The observations are reported as "simultaneous coverage" without mention of detection or non-detection (although non-detection is implied). In a revised version of the manuscript it would be valuable to see these non-detections presented more centrally and directly -- see individual sections for locations where this would be particularly helpful to the reader.

>>> Thank you for helping highlight the most interesting part of the analysis. We will work to raise the profile of the nondetection results as suggested.

@@

>>> Done. The last comment was a bit unclear to me. After rewording, I decided to use a letter footnote symbol for all nondetections and keep the * symbol to denote the Arecibo detection.

2.1 VLA:

A. It would be nice to see the details contained in paragraph 2 of this subsection (as well as the observing setup description paragraphs of other subsections) summarized in a table with information like center observing frequency, bandwidth, time resolution, frequency resolution, dispersion smearing, sensitivity, FWHM, etc.

>>> We have added a new table that summarizes the observing setup for all telescopes discussed here. We also made some small cuts to the text that summarized the observing setup to improve readability and remove some redundancy with this new table.

### 2017-07-18 repeater-vladata.tex
added table of obs configs

The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA. We coordinated observing between the VLA, Arecibo, Effelsberg, LWA1, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}. Below, we summarize these observations, with a focus on those conducted simultaneously with VLA burst detections from \frb.

@@

\startlongtable
\begin{deluxetable}{lcccc}
\small
\tablecaption{Table of VLA Observations \label{tab:obs}}
%\centering
%\begin{tabular}{lcccccc}
\startdata
MJD & Date/time & Duration & Freq. & Bursts \\
 & (ymd/hms) & (min) & (GHz) & \\ \hline
57351 & 2015-11-25/03:25:29 & 60 & 1.4 & 0 \\
57357 & 2015-12-01/05:31:31 & 60 & 1.4 & 0 \\
57359 & 2015-12-03/02:53:57 & 60 & 1.4 & 0 \\
57361 & 2015-12-05/04:45:44 & 60 & 1.4 & 0 \\
57363 & 2015-12-07/04:37:50 & 60 & 1.4 & 0 \\
57365 & 2015-12-09/09:29:25 & 60 & 1.4 & 0 \\
57367 & 2015-12-11/09:22:27 & 60 & 1.4 & 0 \\
57369 & 2015-12-13/09:13:07 & 60 & 1.4 & 0 \\
57371 & 2015-12-15/09:06:16 & 60 & 1.4 & 0 \\
57373 & 2015-12-17/08:57:51 & 60 & 1.4 & 0 \\
57503 & 2016-04-25/23:21:39 & 240 & 3 & 0  \\
57504 & 2016-04-26/23:14:31 & 120 & 3 & 0  \\
57505 & 2016-04-27/23:26:09 & 120 & 3 & 0  \\
57506 & 2016-04-28/22:41:31 & 120 & 3 & 0  \\
57507 & 2016-04-29/22:37:34 & 120 & 3 & 0  \\
57508 & 2016-04-30/19:14:46 & 60 & 3 & 0  \\
57510 & 2016-05-02/23:14:18 & 60 & 3 & 0 \\
57511 & 2016-05-03/22:53:26 & 60 & 3 & 0  \\
57514 & 2016-05-06/18:25:12 & 60 & 3 & 0  \\
57515 & 2016-05-07/19:34:13 & 60 & 3 & 0  \\
57516 & 2016-05-08/19:30:20 & 60 & 3 & 0  \\
57521 & 2016-05-13/17:12:48 & 135 & 3 & 0  \\
57522 & 2016-05-14/17:14:11 & 135 & 3 & 0  \\
57523 & 2016-05-15/17:15:26 & 135 & 3 & 0  \\
57524 & 2016-05-16/16:59:52 & 135 & 3 & 0  \\
57528 & 2016-05-20/16:45:46 & 135 & 3 & 0  \\
57529 & 2016-05-21/16:44:06 & 135 & 3 & 0  \\
57530 & 2016-05-22/16:43:53 & 135 & 3 & 0  \\
57531 & 2016-05-23/16:44:11 & 135 & 3 & 0  \\
57535 & 2016-05-27/16:29:34 & 135 & 3 & 0  \\
57623 & 2016-08-23/17:26:28 & 54 & 3 & 1  \\
57633 & 2016-09-02/15:52:17 & 54 & 3 & 2  \\
57638 & 2016-09-07/10:14:50 & 120 & 3 & 1  \\
57639 & 2016-09-08/10:14:40 & 120 & 3 & 0  \\
57641 & 2016-09-10/09:59:36 & 120 & 3 & 0  \\
57642 & 2016-09-11/09:59:49 & 120 & 3 & 0  \\
57643 & 2016-09-12/09:15:19 & 120 & 3 & 1\tablenotemark{a} \\ 
57644 & 2016-09-13/09:23:59 & 120 & 3 & 0  \\
57645 & 2016-09-14/09:20:23 & 120 & 3 & 1\tablenotemark{a,b} \\
57646 & 2016-09-15/09:16:29 & 120 & 3 & 1  \\
57647 & 2016-09-16/09:11:23 & 120 & 3 & 0  \\
57648 & 2016-09-17/08:59:20 & 120 & 3 & 1\tablenotemark{a,*,c,d} \\ 
57649 & 2016-09-18/08:59:27 & 120 & 3 & 1\tablenotemark{a,b,c,d} \\
57650 & 2016-09-19/08:44:32 & 120 & 3 & 0  \\
57651 & 2016-09-20/08:44:33 & 120 & 3 & 0  \\
57651 & 2016-09-20/17:19:03 & 120 & 6 & 0  \\
57652 & 2016-09-21/09:13:57 & 120 & 6 & 0  \\
57653 & 2016-09-22/09:12:24 & 120 & 6 & 0  \\ \hline
\enddata
\tablecomments{Times are in UT. Duration includes overhead, which is typically 15\%. Frequency is the approximate center of the bandwidth.}
\tablenotetext{a}{AMI-LA nondetection at 15~GHz.}
\tablenotetext{b}{Arecibo nondetection at 1.4~GHz.}
\tablenotetext{*}{Arecibo detection at 1.4~GHz.}
\tablenotetext{c}{Effelsberg nondetection at 4.5~GHz.}
\tablenotetext{d}{LWA1 nondetection near 62 and 78~MHz.}
%\end{tabular}
%\tablenotetext{a}{}
%\label{tab:obs}
\end{deluxetable}

@@

All VLA fast-sampled data were observed with 5~ms sampling, 256 frequency channels, and dual-circular polarization \citep{2015ApJ...807...16L}. The total bandwidths at L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were 256, 1024, and 2048~MHz, respectively, corresponding to channel bandwidths of  1, 4, and 8~MHz. The dispersion smearing across a channel is $\sim1.7$, 0.7, and 0.2~ms in the same respective bands. The 3~GHz data were recorded in eight spectral windows with 32 channels each and had a sensitivity of 5~mJy in 5~ms ($1\sigma$).

@@

@@

Arecibo observed with the L-wide receiver using the PUPPI pulsar backend. The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$). We recorded intnsities of the each of the two orthogonal linear polarization signals and their cross product. Full Stokes polarization intensity spectra can then be generated with a time resolution of 10.24~$\mu$s. Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, significantly reducing intra-channel dispersion smearing. The full width at half maximum (FWHM) beam size at band center is 3.3\arcmin.

@@

Effelsberg observations were conducted with the S60mm receiver and recorded total intensity spectra with the PFFTS backend in pulsar search mode. The observations had a time resolution of 65.5~$\mu$s and 128 frequency channels. The receiver has a system equivalent flux density of 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.

Five Effelsberg observations were made pointing at the known location of \frb\ and had some simultaneous coverage with the VLA. Two of these observations were simultaneous with VLA bursts. The nominal receiver bandwidth is from 4.6 to 5.1~GHz, but a configuration error reduced effective bandwidth to 100~MHz centered at 4.85~GHz for both of these observations during VLA bursts. The sensitivity in these observations was about 28 mJy in 2 ms ($1\sigma$), which is two times worse than the full-bandwidth value. No burst was detected in either of the two observations that were simultaneous with a VLA burst detection.

@@

The LWA1 observations consisted of a single phased-array beam centered on the location of \frb\ with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz. The observations were taken in a spectrometer mode with a channel size of 4.8~kHz and a sample time of 160~ms. The integration time was set to be equal to the dispersion smearing across a single channel at 50~MHz for DM$\approx560$\ pc cm$^{-3}$.

>>>>

The data presented here were obtained from multiple programs and telescopes with a goal of interferometrically localizing \frb\ with the VLA. We coordinated observing between the VLA, Arecibo, Effelsberg, LWA1, and AMI-LA telescopes, as shown in Figure \ref{fig:sched} and Table \ref{tab:obs}. Table \ref{tab:setup} summarizes the instrument configurations for all observations presented here.

@@

\startlongtable
\begin{deluxetable}{lcccc}
\small
\tablecaption{VLA Observations of \frb\ \label{tab:obs}}
%\centering
%\begin{tabular}{lcccccc}
\tablehead{
\colhead{MJD} & \colhead{Date/time} & \colhead{Duration} & \colhead{Freq.} & \colhead{Bursts} \\
\colhead{} & \colhead{(ymd/hms)} & \colhead{(min)} & \colhead{(GHz)} & \colhead{}
}
\startdata
57351 & 2015-11-25/03:25:29 & 60 & 1.4 & 0 \\
57357 & 2015-12-01/05:31:31 & 60 & 1.4 & 0 \\
57359 & 2015-12-03/02:53:57 & 60 & 1.4 & 0 \\
57361 & 2015-12-05/04:45:44 & 60 & 1.4 & 0 \\
57363 & 2015-12-07/04:37:50 & 60 & 1.4 & 0 \\
57365 & 2015-12-09/09:29:25 & 60 & 1.4 & 0 \\
57367 & 2015-12-11/09:22:27 & 60 & 1.4 & 0 \\
57369 & 2015-12-13/09:13:07 & 60 & 1.4 & 0 \\
57371 & 2015-12-15/09:06:16 & 60 & 1.4 & 0 \\
57373 & 2015-12-17/08:57:51 & 60 & 1.4 & 0 \\
57503 & 2016-04-25/23:21:39 & 240 & 3 & 0  \\
57504 & 2016-04-26/23:14:31 & 120 & 3 & 0  \\
57505 & 2016-04-27/23:26:09 & 120 & 3 & 0  \\
57506 & 2016-04-28/22:41:31 & 120 & 3 & 0  \\
57507 & 2016-04-29/22:37:34 & 120 & 3 & 0  \\
57508 & 2016-04-30/19:14:46 & 60 & 3 & 0  \\
57510 & 2016-05-02/23:14:18 & 60 & 3 & 0 \\
57511 & 2016-05-03/22:53:26 & 60 & 3 & 0  \\
57514 & 2016-05-06/18:25:12 & 60 & 3 & 0  \\
57515 & 2016-05-07/19:34:13 & 60 & 3 & 0  \\
57516 & 2016-05-08/19:30:20 & 60 & 3 & 0  \\
57521 & 2016-05-13/17:12:48 & 135 & 3 & 0  \\
57522 & 2016-05-14/17:14:11 & 135 & 3 & 0  \\
57523 & 2016-05-15/17:15:26 & 135 & 3 & 0  \\
57524 & 2016-05-16/16:59:52 & 135 & 3 & 0  \\
57528 & 2016-05-20/16:45:46 & 135 & 3 & 0  \\
57529 & 2016-05-21/16:44:06 & 135 & 3 & 0  \\
57530 & 2016-05-22/16:43:53 & 135 & 3 & 0  \\
57531 & 2016-05-23/16:44:11 & 135 & 3 & 0  \\
57535 & 2016-05-27/16:29:34 & 135 & 3 & 0  \\
57623 & 2016-08-23/17:26:28 & 54 & 3 & 1  \\
57633 & 2016-09-02/15:52:17 & 54 & 3 & 2  \\
57638 & 2016-09-07/10:14:50 & 120 & 3 & 1  \\
57639 & 2016-09-08/10:14:40 & 120 & 3 & 0  \\
57641 & 2016-09-10/09:59:36 & 120 & 3 & 0  \\
57642 & 2016-09-11/09:59:49 & 120 & 3 & 0  \\
57643 & 2016-09-12/09:15:19 & 120 & 3 & 1\tablenotemark{a} \\ 
57644 & 2016-09-13/09:23:59 & 120 & 3 & 0  \\
57645 & 2016-09-14/09:20:23 & 120 & 3 & 1\tablenotemark{a,b} \\
57646 & 2016-09-15/09:16:29 & 120 & 3 & 1  \\
57647 & 2016-09-16/09:11:23 & 120 & 3 & 0  \\
57648 & 2016-09-17/08:59:20 & 120 & 3 & 1\tablenotemark{a,*,c,d} \\ 
57649 & 2016-09-18/08:59:27 & 120 & 3 & 1\tablenotemark{a,b,c,d} \\
57650 & 2016-09-19/08:44:32 & 120 & 3 & 0  \\
57651 & 2016-09-20/08:44:33 & 120 & 3 & 0  \\
57651 & 2016-09-20/17:19:03 & 120 & 6 & 0  \\
57652 & 2016-09-21/09:13:57 & 120 & 6 & 0  \\
57653 & 2016-09-22/09:12:24 & 120 & 6 & 0  \\ \hline
\enddata
\tablecomments{Times are in UT. Duration includes overhead, which is typically 15\%. Frequency is the approximate center of the bandwidth.}
\tablenotetext{a}{AMI-LA nondetection at 15~GHz.}
\tablenotetext{b}{Arecibo nondetection at 1.4~GHz.}
\tablenotetext{*}{Arecibo detection at 1.4~GHz.}
\tablenotetext{c}{Effelsberg nondetection at 4.5~GHz.}
\tablenotetext{d}{LWA1 nondetection near 62 and 78~MHz.}
%\end{tabular}
%\tablenotetext{a}{}
%\label{tab:obs}
\end{deluxetable}

@@

All VLA fast-sampled data were observed with 5~ms sampling, 256 frequency channels, and dual-circular polarization \citep{2015ApJ...807...16L}. As shown in Table \ref{tab:setup}, the L (1.4~GHz), S (3~GHz), and C (6~GHz) bands were used with channel resolutions that kept dispersion smearing well below the temporal resolution. All detections were made in the 3~GHz data, which were recorded in eight spectral windows with 32 channels each and had a sensitivity of 4~mJy in 5~ms ($1\sigma$).

@@

\begin{deluxetable*}{lcccccc}
\tablecaption{Observing Configurations \label{tab:setup}}
\startdata
\tablehead{
\colhead{Telescope} & \colhead{Freq. Center} & \colhead{Freq. Bandwidth} & \colhead{Freq. Resolution} & \colhead{Time resolution} & \colhead{DM smearing\tablenotemark{a}} & \colhead{Sensitivity} \\
\colhead{}     & \colhead{(GHz)} & \colhead{(MHz)} & \colhead{(MHz)} & \colhead{(ms)} & \colhead{(ms)} & \colhead{($1\sigma$; Jy ms)}
}
LWA        & 0.062/0.078\tablenotemark{b} & 19.6 & 0.0048 & 160 & 83/43 & 9600 \\
Arecibo    & 1.44 & 580 & 1.5625 & 0.01024 & 0.0\tablenotemark{c} & 0.004 \\
VLA        & 1.4  & 256  & 1     & 5       & 1.7 & 0.050 \\
VLA        & 3.0  & 1024 & 4     & 5       & 0.7 & 0.020 \\
VLA        & 6.0  & 2048 & 8     & 5       & 0.2 & 0.013 \\
Effelsberg & 4.85 & 100  & 0.8   & 0.0655 & 0.032 & 0.056 \\
AMI-LA     & 15   & 5000 & 625   & 1e3     & 0.0 & 30 \\ \hline
\enddata
%\tablecomments{}
\tablenotetext{a}{DM smearing calculated for nominal \frb\ DM of 560.5 pc cm$^{-3}$ at the center frequency.}
\tablenotetext{b}{LWA1 observed with two independent bands with identical configurations and sensitivities.}
\tablenotetext{c}{Arecibo data are coherently dedispersed to 560.5 pc cm$^{-3}$, so DM smearing is effectively eliminated.}
\end{deluxetable*}

@@

Arecibo observed with the L-wide receiver using the PUPPI pulsar backend \citep{2008SPIE.7019E..1DD,2010SPIE.7740E..0AF}. The observational frequency range was 1.15 to 1.73~GHz and frequency resolution was 1.5625~MHz, which has a typical sensitivity of 2~mJy in 2~ms ($1\sigma$). We recorded intnsities of the each of the two orthogonal linear polarization signals and their cross product. Full Stokes polarization intensity spectra can then be generated with a time resolution of 10.24~$\mu$s. Each frequency channel was coherently dedispersed to 557~pc cm$^{-3}$, significantly reducing intra-channel dispersion smearing. The full width at half maximum (FWHM) beam size at band center is 3.3\arcmin.

@@

Effelsberg observations were conducted with the S60mm receiver and recorded total intensity spectra with the PFFTS backend in pulsar search mode with a time resolution of 65.5~$\mu$s. The receiver has a system equivalent flux density of 18 Jy and a FWHM beam size of 2.4\arcmin\ at 4.85~GHz.

Five Effelsberg observations were made pointing at the known location of \frb\ and had some simultaneous coverage with the VLA. Two of these observations were simultaneous with VLA bursts, but made no detection. The nominal receiver bandwidth is from 4.6 to 5.1~GHz, but a configuration error reduced effective bandwidth to 100~MHz centered at 4.85~GHz for both of these observations during VLA bursts. The sensitivity in these observations was about 28 mJy in 2 ms ($1\sigma$), which is two times worse than the full-bandwidth value. No burst was detected in either of the two observations that were simultaneous with a VLA burst detection.

@@

The LWA1 observations consisted of a single phased-array beam centered on the location of \frb\ with two 4096-channel spectral windows spanning frequencies from 52.2--71.8~MHz and 68.2--87.8~MHz. The sample time of 160~ms was set to be equal to the dispersion smearing across a single channel at 50~MHz for DM$\approx560$\ pc cm$^{-3}$.
